### 2020-07-16 paper.Rmd
using one plot to illustrate the criteria in the example instead of two

```{r, fig.cap = "Illustrates the 1-to-1 relationship between SSE and difference in means (Panel A) and variance (Panel B). Each data point illustrates a partition, i.e., a way to divide a data set ($N = 14$) into two groups.", fig.height = 3.5}

@@

# Plot relationship between objectives
par(mfrow = c(1, 2))
plot(
  all_objectives_mean, 
  all_objectives_kMeans, 
  xlab = "mean(f1) - mean(f2)",
  ylab = "SSE",
  pch = 4, 
  cex = .5,
  col = "darkgrey"
)
legend("topright", legend = "A", cex = 1.3, bty = "n")
plot(
  all_objectives_var, 
  all_objectives_kVar, 
  xlab = "var(f1) - var(f2)",
  ylab = "SSE_var",
  pch = 4, 
  cex = .5,
  col = "darkgrey"
)
legend("topright", legend = "B", cex = 1.3, bty = "n")
```

```{r, fig.width = 4.5, fig.height = 4.5, fig.cap = "All partitions. Points = pareto efficient set."}

# Plot SSE vs SSE(VAR)
plot(
  df, pch = 4, col = "darkgrey", 
  las = 1, cex = .5,
  xlab = "mean(f1) - mean(f2)",
  ylab = "var(f1) - var(f2)"
)

>>>>

```{r, fig.cap = "Illustrates the 1-to-1 relationship between SSE and difference in means (Panel A) and variance (Panel B). Each data point illustrates a partition, i.e., a way to divide a data set ($N = 14$) into two groups. In Panel C, the relationship between the two criteria across partitions is plotted. The highlighted symbols indicate membership of the pareto set. The partition represented by the diamond minimizes the difference in variances between groups; the partition represented by the square minimizes the difference in means between groups; the partition represented by the triangular minimizes the sum of the differences in means and variances. ", fig.height = 7, fig.width = 6}

@@

# Plot relationship between objectives
layout(matrix(c(1,2,3,3), 2, 2, byrow = TRUE), heights = c(1, 1.4))
plot(
  all_objectives_mean, 
  all_objectives_kMeans, 
  xlab = "mean(f1) - mean(f2)",
  ylab = "SSE",
  pch = 4, 
  cex = .5,
  col = "darkgrey"
)
legend("topright", legend = "A", cex = 1.3, bty = "n")
plot(
  all_objectives_var, 
  all_objectives_kVar, 
  xlab = "var(f1) - var(f2)",
  ylab = "SSE_var",
  pch = 4, 
  cex = .5,
  col = "darkgrey"
)
legend("topright", legend = "B", cex = 1.3, bty = "n")

par(mar = c(7, 10, 0.4, 8) + 0.1)

# Plot SSE vs SSE(VAR)
plot(
  df, pch = 4, col = "darkgrey", 
  las = 1, cex = .5,
  xlab = "mean(f1) - mean(f2)",
  ylab = "var(f1) - var(f2)"
)
legend("topright", legend = "C", cex = 1.3, bty = "n")
